Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-07-11 man/tables/t_forest_history.Rmd
update

@Catastro1752; @MesaTorres2009; @Bonet2014_conama
@Bonet2014_conama; @MorenoLlorca2016; @CMA2018
@Bonet2016obsnev_forest; @MorenoLlorca2016; J. Navarro and F.J. Cano-Manuel *personal communications*
@Cruz1991; @Wing2015
@JimenezOlivencia2015; @2015Zoido; @MorenoLlorca2016; @Calatrava2019
@Maestre1852; @Maestre1858; @Titos1990; @MesaTorres2009
@Navarro2014
@MartinCivantos2014; @MartinMontanes2015; @RuizRuiz2017
@Catastro1752; @Lopez1776; @Madoz1846; @Titos1997; @Ferrer1999; @MesaTorres2009; @Bonet2014_conama

>>>>

@Catastro1752; @MesaTorres2009; @Bonet2014_conama
@Bonet2014_conama; @MorenoLlorca2016; @CMA2018
@Bonet2016obsnev_forest; @MorenoLlorca2016; J. Navarro and F.J. Cano-Manuel *personal communications*
@Cruz1991; @Wing2015
@JimenezOlivencia2015; @2015Zoido; @MorenoLlorca2016; @Calatrava2019
@Maestre1852; @Maestre1858; @Titos1990; @MesaTorres2009
@Navarro2014
@MartinCivantos2014; @MartinMontanes2015; @RuizRuiz2017
@Catastro1752; @Lopez1776; @Madoz1846; @Titos1997; @Ferrer1999; @MesaTorres2009; @Bonet2014_conama
@JimenezSerrano2004; @RomeroZurbano1909; @Arnedo2007
